### 2020-03-02 Hands-on Machine Learning/16_Interpretable-Machine-Learning.rmd
frm ch1
frm ch1

---
title: ''
mainfont: Arial
fontsize: 12pt
documentclass: report
header-includes:
- \PassOptionsToPackage{table}{xcolor}
- \usepackage{caption}
- \usepackage{amssymb}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage[table]{xcolor}
- \usepackage{fancyhdr}
- \usepackage{boldline}
- \usepackage{tipa}
   \definecolor{headergrey}{HTML}{545454}
   \definecolor{msdblue}{HTML}{1C93D1}
   \pagestyle{fancy}
   \setlength\headheight{30pt}
   \rhead{\color{headergrey}\today}
   \fancyhead[L]{\color{headergrey}Moretz, Brandon}
   \fancyhead[C]{\Large\bfseries\color{headergrey}Stacked Models}
   \rfoot{\color{headergrey}\thepage}
   \lfoot{\color{headergrey}Chapter 15}
   \fancyfoot[C]{\rmfamily\color{headergrey}Hands-On Machine Learning}
geometry: left = 1cm, right = 1cm, top = 2cm, bottom = 3cm
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    fig_caption: yes
    latex_engine: xelatex
editor_options: 
  chunk_output_type: console
fig_width: 9
fig_height: 3.5
---

@@

# Resampling & Modeling
library(MASS, quietly = TRUE, warn.conflicts = FALSE)
library(rsample, quietly = TRUE, warn.conflicts = FALSE)
library(caret, quietly = TRUE, warn.conflicts = FALSE)
library(h2o, quietly = TRUE, warn.conflicts = FALSE)
library(forecast, quietly = TRUE, warn.conflicts = FALSE)
library(vip, quietly = TRUE, warn.conflicts = FALSE)
library(pdp, quietly = TRUE, warn.conflicts = FALSE)
library(kernlab, quietly = TRUE, warn.conflicts = FALSE)
library(mlbench, quietly = TRUE, warn.conflicts = FALSE)

@@

## Stacked Models

>>>>

---
title: ''
mainfont: Arial
fontsize: 12pt
documentclass: report
header-includes:
- \PassOptionsToPackage{table}{xcolor}
- \usepackage{caption}
- \usepackage{amssymb}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage[table]{xcolor}
- \usepackage{fancyhdr}
- \usepackage{boldline}
- \usepackage{tipa}
   \definecolor{headergrey}{HTML}{545454}
   \definecolor{msdblue}{HTML}{1C93D1}
   \pagestyle{fancy}
   \setlength\headheight{30pt}
   \rhead{\color{headergrey}\today}
   \fancyhead[L]{\color{headergrey}Moretz, Brandon}
   \fancyhead[C]{\Large\bfseries\color{headergrey}Interpretable Machine Learning}
   \rfoot{\color{headergrey}\thepage}
   \lfoot{\color{headergrey}Chapter 16}
   \fancyfoot[C]{\rmfamily\color{headergrey}Hands-On Machine Learning}
geometry: left = 1cm, right = 1cm, top = 2cm, bottom = 3cm
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    fig_caption: yes
    latex_engine: xelatex
editor_options: 
  chunk_output_type: console
fig_width: 9
fig_height: 3.5
---

@@

# Resampling & Modeling
library(MASS, quietly = TRUE, warn.conflicts = FALSE)
library(rsample, quietly = TRUE, warn.conflicts = FALSE)
library(caret, quietly = TRUE, warn.conflicts = FALSE)
library(h2o, quietly = TRUE, warn.conflicts = FALSE)
library(forecast, quietly = TRUE, warn.conflicts = FALSE)
library(pdp, quietly = TRUE, warn.conflicts = FALSE)
library(kernlab, quietly = TRUE, warn.conflicts = FALSE)
library(mlbench, quietly = TRUE, warn.conflicts = FALSE)

library(vip, quietly = TRUE, warn.conflicts = FALSE)
library(pdp, quietly = TRUE, warn.conflicts = FALSE)
library(iml, quietly = TRUE, warn.conflicts = FALSE)
library(DALEX, quietly = TRUE, warn.conflicts = FALSE)
library(lime, quietly = TRUE, warn.conflicts = FALSE)

@@

## Interpretable Machine Learning
